# TOPIC MODELS

[BERTopic](https://maartengr.github.io/BERTopic/getting_started/topicsovertime/topicsovertime.html) 

So far, I have only run this in enviro speeches. 

```{r topic clusters, echo=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/plot_topics_150_original.html",
  scrolling = "yes",
  frameBorder = "0",
  height=800,
  width="100%"
)

```

```{r topic clusters intertopic map, echo=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/plot_topics_150_mmr.html",
  scrolling = "yes",
  frameBorder = "0",
  height=800,
  width="100%"
)

```

## topic representation

different [topic representations](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html) take different approaches to assigning topic labels. the two I have used, in addition the default approach, are (1) the [KeyBERTInspired](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#keybertinspired) topic representation and (2) the [MaximalMarginalRelevance](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#maximalmarginalrelevance)
topic representation.

[KeyBERT](https://maartengr.github.io/BERTopic/getting_started/ctfidf/ctfidf.html) (default): assigns topic labels based on most distinguishing words in the topic (similar to ip-idf).

[KeyBERTInspired:](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#keybertinspired) does something extra, still trying to understand.

[MaximalMarginalRelevance:](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#maximalmarginalrelevance) reduces redundancy of selected topic keywords (e.g., car vs. cars)

[OpenAI](https://maartengr.github.io/BERTopic/getting_started/representation/llm.html#openai) (trying to get this to work): supplies ChatGBT with a representative selection of topic documents and keywords and asks it to return a 5-10 word topic label.

```{r topics, echo=FALSE}

topic_info <- read_csv("data/topic_info_150_reduceOutliers.csv") %>%
  as_tibble()

topic_info

```


## topic hierarchy

#### topic representation: default

```{r topic cluster hierarchy, echo=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/plot_topics_hierarchy_150.html",
  scrolling = "yes",
  frameBorder = "0",
  height=800,
  width="100%"
)

```


#### topic representation: [KeyBERTInspired](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#keybertinspired)

```{r topic clusters key, echo=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/plot_topics_hierarchy_150_key.html",
  scrolling = "yes",
  frameBorder = "0",
  height=800,
  width="100%"
)

```


#### topic representation: [MaximalMarginalRelevance](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#maximalmarginalrelevance)

```{r topic clusters mmr, echo=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/plot_topics_hierarchy_150_mmr.html",
  scrolling = "yes",
  frameBorder = "0",
  height=800,
  width="100%"
)

```

## topics over time

### 10-yr

#### topic representation: [KeyBERTInspired](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#keybertinspired)
```{r 10yr topic clusters over time key, echo=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/plot_topics_over_time_150_10_key.html",
  scrolling = "yes",
  frameBorder = "0",
  height=800,
  width="100%"
)

```


#### topic representation: [MaximalMarginalRelevance](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#maximalmarginalrelevance)

```{r 10yr topic clusters over time MMR, echo=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/plot_topics_over_time_150_10_mmr.html",
  scrolling = "yes",
  frameBorder = "0",
  height=800,
  width="100%"
)

```

### 5-yr

#### topic representation: [KeyBERTInspired](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#keybertinspired)
```{r 5yr topic clusters over time key, echo=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/plot_topics_over_time_150_5_key.html",
  scrolling = "yes",
  frameBorder = "0",
  height=800,
  width="100%"
)

```


#### topic representation: [MaximalMarginalRelevance](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#maximalmarginalrelevance)

```{r 5yr topic clusters over time MMR, echo=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/plot_topics_over_time_150_5_mmr.html",
  scrolling = "yes",
  frameBorder = "0",
  height=800,
  width="100%"
)

```

### 2-yr

#### topic representation: [KeyBERTInspired](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#keybertinspired)
```{r 2yr topic clusters over time key, echo=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/plot_topics_over_time_150_2_key.html",
  scrolling = "yes",
  frameBorder = "0",
  height=800,
  width="100%"
)

```


#### topic representation: [MaximalMarginalRelevance](https://maartengr.github.io/BERTopic/getting_started/representation/representation.html#maximalmarginalrelevance)

```{r 2yr topic clusters over time MMR, echo=FALSE, cache=TRUE}

tags$iframe(
  src = "figures/plot_topics_over_time_150_2_mmr.html",
  scrolling = "yes",
  frameBorder = "0",
  height=800,
  width="100%"
)

```


